Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-14 README.Rmd
more small changes

`bullet-train`: A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features from the Hamby 173 and 252 sets (XXX reference XXX). This dataset is created using the data available XXX, which contains XXX (add more info about the comparisons). The only changes made to the data from XXX were to remove any lands with tank rash, select only variables of use for the paper, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons. The variables in the data are as follows:

@@

`bullet-test`: A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from sets 1 and 11 of the Hamby 224 Clone sets (XXX reference XXX). Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. Each bullet has 6 lands. The data contains comparisons of bullet-lands within a set. With three bullets with six lands per set, there are a total of (2 sets) x (3! bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons. However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data. This is due to the fact that some of the lands are missing from the data (probably due to tank rank): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11. The `r dim(bullet_test)[2]` variables in the data are the same as those in the training data (see the variable definitions associated with `bullet-train`).

`example-signatures`: Contains the signature data from two bullet-land signatures that are a match. The variables in the data are as follows:

>>>>

**`bullet-train`**

A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features from the Hamby 173 and 252 sets (XXX reference XXX). This dataset is created using the data available at XXX, which contains XXX (add more info about the comparisons). The only changes made to the data from XXX were to remove any lands with tank rash, select only variables of use for the paper, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons. The variables in the data are as follows:

@@

**`bullet-test`**

A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from sets 1 and 11 of the Hamby 224 Clone sets (XXX reference XXX). Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. Each bullet has 6 lands. The data contains comparisons of bullet-lands within a set. With three bullets with six lands per set, there are a total of (2 sets) x (3! bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons. However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data. This is due to the fact that some of the lands are missing from the data (probably due to tank rank): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11. The `r dim(bullet_test)[2]` variables in the data are the same as those in the training data (see the variable definitions associated with `bullet-train`).

**`example-signatures`**

Contains the signature data from two bullet-land signatures that are a match. The variables in the data are as follows:
